Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-21 chap-intro.tex
More revisions to summary

This thesis is divided into three parts:
\begin{itemize}
\item In \cref{part:ch-aosd13}, we describe work on optimizing collection
  queries by static program transformation, based on a set of rewrite rules~\citep{GiarrussoAOSD13}.
\item In \cref{part:incr}, we describe work on incrementalizing programs
  by static program transformation. This thesis presents the first approach that
  handles higher-order programs by using program transformation; hence, while
  our main examples use collection queries, we phrase the work in terms of
  $\lambda$-calculi with unspecified primitives~\citep*{CaiEtAl2014ILC}.
  In \cref{ch:cts}, we extend ILC with a further program transformation
  step, so that base programs can store intermediate results and derivatives can
  reuse them, but without resorting to dynamic memoization and necessarily
  needing to look results up at runtime. To this end, we build on work by
\citet{Liu00} and extend it to a higher-order, typed setting.
\end{itemize}

@@

\subsection{Navigating this thesis}
\pg{WIP!!}
Many chapters are independent from each other, with a few exceptions.
\Cref{part:ch-aosd13} can be read independently from the rest.

% Write this even though maybe I restructure the parts.
\Cref{part:incr} describes incrementalization.

\paragraph{Differentiation}
\Cref{sec:intro} and \cref{ch:diff-examples} introduce the overall approach to
incrementalization informally.

The core mathematical theory underlying incrementalization correctness using ILC
is developed formally in \cref{ch:derive-formally} and~\cref{ch:change-theory}
using a denotational framework. Equational reasoning on terms is then developed
in~\cref{sec:term-reasoning}. These chapters contain full formal proofs: readers
are welcome to skip or skim those proofs where appropriate. We strive not to
hide important definitions inside theorems, and to give stand-alone definitions
and theorem statements.

>>>>

\pg{Rewrite}
This thesis is divided into two parts:
\begin{itemize}
\item In \cref{part:ch-aosd13}, we describe work on optimizing collection
  queries by static program transformation, based on a set of rewrite rules~\citep{GiarrussoAOSD13}.
\item In \cref{part:incr}, we describe work on incrementalizing programs
  by static program transformation. This thesis presents the first approach that
  handles higher-order programs by using program transformation; hence, while
  our main examples use collection queries, we phrase the work in terms of
  $\lambda$-calculi with unspecified primitives~\citep*{CaiEtAl2014ILC}.
  In \cref{ch:cts}, we extend ILC with a further program transformation
  step, so that base programs can store intermediate results and derivatives can
  reuse them, but without resorting to dynamic memoization and necessarily
  needing to look results up at runtime. To this end, we build on work by
\citet{Liu00} and extend it to a higher-order, typed setting.
\end{itemize}

@@

\subsection{Navigating this thesis}
\pg{WIP!!}
Many chapters are independent from each other, with a few exceptions.
\Cref{part:ch-aosd13} can be read independently from the rest.
% Write this even though maybe I restructure the parts.
\Cref{part:incr} describes incrementalization.

\paragraph{Differentiation}
\Crefrange{sec:intro}{sec:term-reasoning} form the core of incrementalization
theory, with other chapters building on top of them.

\Cref{sec:intro} and \cref{ch:diff-examples} introduce the overall approach to
incrementalization informally.

\Cref{ch:derive-formally,ch:change-theory} show that incrementalization using
ILC is correct. Building on a set-theoretic semantics, these
\lcnamecrefs{ch:derive-formally} also develop the theory
underlying this correctness proofs and further results.

Equational reasoning on terms is then developed
in \cref{sec:term-reasoning}. These chapters contain full formal proofs: readers
are welcome to skip or skim those proofs where appropriate. We strive not to
hide important definitions inside theorems, and to give stand-alone definitions
and theorem statements.
